Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-26 fully-abstract-comp/technical-report.tex
fixed store bug ?
Add a comment and fix a typo.

The source machine is also a capability machine with memory capabilities and sealed capabilities. Unlike the target machine, the source machine is going to have a built in stack along with special stack and return capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    n & \in & \nats \\
    \src{r} &\in &  \RegName \setminus \{\rstk\}\\
    \src{\rn} &\defbnf & \src{r} \mid n \\
    \src{i} & \defbnf &  \trg{i} \mid \scall{\src{r}}{\src{r}}
  \end{array}
\]
\lau{30-08-2017: We had $\rret$ as not being one of the registers on the source machine. I could not recall why we had this, so I removed it. (I think it may have been from when we had call and return instructions?)}
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{}{}$ instruction.

@@

\subsection{Operational Semantics}
\subsubsection{Notes}
Genrally:
\begin{itemize}
%\item Opaque capabilities: Only allow locality and permission to be inspected (i.e., no addresses disclosed).
\item Linear capabilities are cleared when they move around in memory.
\end{itemize}

@@

\noindent\textbf{store}\\
\begin{align*}
  \sem{\tstore{r_1}{r_2}}(\Phi) = &
                                    \begin{cases}
                                      \updPcAddr{}\left(
                                        \arraycolsep=0pt
                                        \begin{array}{rl}
                                          \Phi&\updReg{r_2}{w_2}\\
                                              &\update{\mem.a}{w}
                                        \end{array}
\right) & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                        \perm \in \writeAllowed{} \tand\\
                                        \withinBounds{\Phi(r_1)} \tand \\
                                        w = \Phi(r_2) \tand \\
                                        w_2 = \linCons{w}
                                      \end{array}
                                      \\
                                      \sourcecolor\left.
                                      \updPcAddr{}\left(
                                      \arraycolsep=0pt
                                      \begin{array}{rl}
                                        \Phi&\update{\mem.a}{w}\\
                                            &\updReg{r_2}{w_2}
                                      \end{array}
                                      \right) \right.& 
                                      \sourcecolor\left.
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                        \perm \in \writeAllowed{} \tand \\
                                        \withinBounds{\Phi(r_1)} \tand \\
                                        a \in \dom(\Phi.\ms_\stk) \tand \\
                                        w = \Phi(r_2) \\
                                        w_2 = \linCons{w}
                                      \end{array}\right.\\
                                      \failed & \totherwise
                                    \end{cases}
\end{align*}

>>>>

The source machine is also a capability machine with memory capabilities and sealed capabilities. Unlike the target machine, the source machine is going to have a built in stack along with special stack and return capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    n & \in & \nats \\
    \src{r} &\in &  \RegName \setminus \{\rstk\}\\
    \src{\rn} &\defbnf & \src{r} \mid n \\
    \src{i} & \defbnf &  \trg{i} \mid \scall{\src{r}}{\src{r}}
  \end{array}
\]
\lau{30-08-2017: We had $\rret$ as not being one of the registers on the source machine. I could not recall why we had this, so I removed it. (I think it may have been from when we had call and return instructions?)}
\dominique{26-9-2017: I think we should allow $\rstk$ in the source language too.}
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{}{}$ instruction.

@@

\subsection{Operational Semantics}
\subsubsection{Notes}
Generally:
\begin{itemize}
%\item Opaque capabilities: Only allow locality and permission to be inspected (i.e., no addresses disclosed).
\item Linear capabilities are cleared when they move around in memory.
\end{itemize}

@@

\noindent\textbf{store}\\
\begin{align*}
  \sem{\tstore{r_1}{r_2}}(\Phi) = &
                                    \begin{cases}
                                      \updPcAddr{}\left(
                                        \arraycolsep=0pt
                                        \begin{array}{rl}
                                          \Phi&\updReg{r_2}{w_2}\\
                                              &\update{\mem.a}{w}
                                        \end{array}
\right) & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                        \perm \in \writeAllowed{} \tand\\
                                        \withinBounds{\Phi(r_1)} \tand \\
                                        w = \Phi(r_2) \tand \\
                                        w_2 = \linCons{w}
                                      \end{array}
                                      \\
                                      \sourcecolor\left.
                                      \updPcAddr{}\left(
                                      \arraycolsep=0pt
                                      \begin{array}{rl}
                                        \Phi&\updReg{r_2}{w_2}\\
                                            &\update{\ms_\stk.a}{w}
                                      \end{array}
                                      \right) \right.& 
                                      \sourcecolor\left.
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                        \perm \in \writeAllowed{} \tand \\
                                        \withinBounds{\Phi(r_1)} \tand \\
                                        \aaddr \in \dom(\Phi.\ms_\stk) \tand \\
                                        w = \Phi(r_2) \\
                                        w_2 = \linCons{w}
                                      \end{array}\right.\\
                                      \failed & \totherwise
                                    \end{cases}
\end{align*}
